maxent model avec xvalidation

### 2019-04-04 src/maxent_avec_xvalidation.Rmd
raster avging started

>>>>

for this bit may need to stack rasters by depth... this will need some working with the name
get unique filenames into a list
ignore the first X characters in the filename (yr_mth_) and stack based on the last bit of the filename
then do something probably with raster package

```{r avg asc layers}
asc_list <- list.files("../output/maxent/predictions/jan", pattern = '*.asc', full.names = TRUE) #true means the full path is included
